---
title: "BPD_911_Calls_Analysis"
author: "Krishna"
date: "2/4/2019"
output:
  html_document: 
    keep_md: yes
---

## Summary

This Shiny Web App analyzes Baltimore police department 911 calls data. See below for further details.

  1. Data source for this anaylsis is from Baltimore Police Data Gov site.
  2. Baltimore 911 calls data is available from year 2015 to current date and this app can analyze all 
     data depening upon available resources.
  3. This Application helps in answering below questions regarding Baltimore 911 calls data.
     a. What type of 911 calls were made over given period?
     b. How many 911 calls data were made per day over given period?
     c. How many 911 calls data were made per hour over given period?
     d. From which incident location, these 911 calls were made?

## Load necessary libraries

```{r}
library(dplyr)
library(tidyr)
library(lubridate)
library(jsonlite)
```

## Data used for this analysis

Fetch JSON format data from Baltimore 911 calls data gov site.

```{r}
p911data <- fromJSON(URLencode("https://data.baltimorecity.gov/resource/m8g9-abgb.json?$where=date_trunc_ymd(calldatetime) between '2015-01-01' AND '2019-02-28'&$limit=5000000"),flatten=TRUE) 
dim(p911data)
```

## Understand data and sample data

```{r}
str(p911data)
head(p911data)
```

## Explore data

```{r}
p911data %>% group_by(callyear=substr(calldatetime,1,4)) %>% summarise(n())
```

## Important Links

### Data Source (JSON Format) 

Baltimore 911 Calls json data api end point link is provided below.

https://data.baltimorecity.gov/resource/m8g9-abgb.json

### Source Code

Baltimore 911 Calls analysis Source code is uploaded to Github and link is provided below.

https://github.com/krishnaitdbg/Baltimore_Police_911_Calls_Analysis

### Analysis output 

Shiny web App is uploaded to Shiny server and link is provided below.

https://krishnaitdbg.shinyapps.io/BPolice_911_Call_Data_Analysis/


Thank you for the visit.